---
title: "Twitter Sentimental Analysis related to Popular Cryptocurrencies"
author: "Keshik"
date: "May 22, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load relevant libraries
```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(dplyr)
library(tidyr)
library(textcat)
library(cldr)
library(sentimentr)
library(MVR)
library(anytime)
```

# Read raw data and process it to prepare for analysis and visualization
```{r warning=FALSE, message=FALSE}
data_file_path <- "E:\\Twitter-Sentimental_Analysis_related_to_Cryptocurrencies\\TweetsData\\tweets"
collection_year <-  "2014"

files_path = paste(data_file_path, collection_year, sep = "")

list_file <- list.files(path = files_path , pattern = "*.csv")

bitcoinPrice <- read.csv(paste("BitcoinPriceData/bitcoin_", collection_year, "_prices.csv", sep = ""), sep = ",")


for (fileName in list_file){
  tweets <- read_csv2(paste(files_path, fileName, sep = "\\"))

  tweets$text <- tweets$text %>%
    str_remove_all("\n") %>%
    str_remove_all("((www\\.[^\\s]+)|(https?://[^\\s]+)|(pic\\.[^\\s]+))") %>%
    str_remove_all('@(\\s+)') %>%
    str_remove_all("^rt+") %>%
    str_remove_all('#(\\s+)') %>%
    str_replace_all('\\s+', " ") %>%
    str_remove_all('"')
  
  tweets <- unique(tweets)
    
  tweets <- tweets %>%
    mutate(language = detectLanguage(documents = tweets$text, isPlainText = TRUE)[,1]) %>%
    filter(language == "ENGLISH") %>%
    mutate(sentimentScore = 0)
  
  tweets <- tweets %>%
    mutate(unixTime = as.integer(as.POSIXct(tweets$date, tz = "GMT")))
  
  filteredPrice <- bitcoinPrice %>%
    select(Timestamp, Weighted_Price)
  
  filteredPrice$Timestamp <- as.numeric(levels(droplevels(filteredPrice$Timestamp)))
    
  tweets <- left_join(tweets, filteredPrice, by= c("unixTime" = "Timestamp"))
  
  for (i in 1:nrow(tweets)){
    DF = sentiment(tweets$text[i])
    DF = DF[complete.cases(DF), ]
    if (nrow(DF) >1){
      tweets$sentimentScore[i] = sum(DF[,3]*DF[,4])/sum(DF[,3])
    }
    else{
      tweets$sentimentScore[i] = sum(DF[1,4])
    }
  }
  
  tweets %>%
    select(username, date, unixTime, text, sentimentScore, Weighted_Price) %>%
    write.csv(file = paste("Processed-tweets/tweets", collection_year ,"/", fileName, sep = ""))
}


```


# References
1. https://www.kaggle.com/mczielinski/bitcoin-historical-data



  hashtags = col_character(),
  id = col_double(),
  permalink = col_character()
)
Modify Chunk OptionsRun Current ChunkModify Chunk OptionsRun All Chunks AboveRun Current ChunkModify Chunk OptionsRun All Chunks AboveRun Current Chunk

			
ConsoleE:/Twitter-Sentimental_Analysis_related_to_Cryptocurrencies/
			





